UAV vs Sentinel-2 height comparisons

### 2023-07-20 submission_3/UAV+S2.qmd
Adds redered pdf of submission 3

---
title: "UAV vs Sentinel-2 height comparisons"
subtitle: "Documentation"
author: "Fabian Götz"
date: 6/24/23
format:
    pdf:
        documentclass: scrreport
        theme: united
        toc: true
        toc-depth: 2
        number-sections: true
        number-depth: 1
        toc-title: Table of Contents
        toc-location: body
        colorlinks: true
header-includes:  
- \usepackage{graphicx}
- \usepackage{lscape}
- \usepackage{array}
---

>>>>

---
title: "UAV vs Sentinel-2 height comparisons"
subtitle: "Documentation"
author:  
    # - **Group 4** 
    - Denis Streitmatter 
    - Marie-Louise Korte 
    - Louis Trinkle 
    - Maxwell Sivertsen 
    - Fabian Götz 
    - Lukas Erzfeld
date: 6/24/23
format:
    pdf:
        documentclass: scrreport
        theme: united
        toc: true
        toc-depth: 2
        number-sections: true
        number-depth: 1
        toc-title: Table of Contents
        toc-location: body
        colorlinks: true
header-includes:  
- \usepackage{graphicx}
- \usepackage{lscape}
- \usepackage{array}
---
